MaxEnt: What is it good for?

### 2015-06-16 ms.tex
hypothesis space
Acknowledgements

@@

@@

>>>>

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
propositions is true, but we don't know which.

@@

\section{A special case: updating given propositions}

@@

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (),
Stephen Gull (),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),
